Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures

### 2020-09-28 1_manuscript/itt-emotion.tex
Add: conclusion, upd: moved chinese keyword list

  % In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels. We extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations. We used these keywords for sentiment classification via an SVC.

  % In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, confirming our hypothesis \ref{hyp:omotenashi_en}. However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction. As such, our hypothesis \ref{hyp:omotenashi_zh} is rejected. Since both cultures have a different reaction to this environment of hospitality, our hypothesis \ref{hyp:omotenashi_both} is confirmed. From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{Omotenashi}. One theory is that they are not being treated well enough, and this environment is not compatible with them because of language or culture barriers. The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way. We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.

  % Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to managerial attributes of a hotel or environmental attributes of the hotel. Managerial attributes are those that they can be changed via managerial decisions without relocating. On the other hand, environmental attributes are things like location, closeness to shops, or public transport. We found that both are included in the satisfaction and dissatisfaction of both customer groups, confirming our hypothesis \ref{hyp:man_env}. We also found that most of the Western customer satisfaction (50\% of the top 10 words) and dissatisfaction (100\% of the top 10 words) stems from managerial attributes of the hotel.

  % In contrast, environmental attributes only make for a smaller portion of the factors (40\% of the top 10 satisfaction keywords). In the case of Chinese customer satisfaction, the top of the list was managerial (30\% of the top 10 words), and a more significant portion, although lower in its ranking, was environmental (40\%). For Chinese customer dissatisfaction, however, 71.4\% of the keywords were managerial, while the other 28.6\% were environmental. We discussed how these distributions in managerial or environmental factors having priorities in either population could lead to different management strategies. One possible approach is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number. They are less satisfied with managerial factors but have an identifiable method of improving satisfaction by lessening language barriers and providing breakfast. Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect, as well as making the hotels tobacco-free. With this strategy, we favor ``long-haul'' Western tourists who spend almost half of their budget on hotels. While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns. The reason for this being that Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased. In this paper, we provide results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan, and we can observe their stark differences and shared attributes.

>>>>

  In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}. To answer our research questions \ref{rsq:omotenashi} and \ref{rsq:omotenashi_both}, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations. We used these keywords for sentiment classification via an SVC, and then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns, as well as single words. We divided this data by sentiment and by hotel price range, considering the most expensive price for a room for one night.

  In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, cleanliness and other attributes relating to services and hospitality of the hotel. However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction, more inclined to praise the room, location or the convenience of the hotel. We found that both cultures have a different reaction to this environment of hospitality, and both cultures have a different way of reacting to different prices. From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{omotenashi}. One theory is that while they are being treated well and they react positively, the environment is not compatible with them because of language or culture barriers and it lessens their experience. The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way. We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented. On the other hand, Western tourists, even when they hold high expectations in a highly priced hotel, show that Japanese hospitality exceeds their expectations, judging by the vocabulary they use for expressing their satisfaction. We consider that Western tourists are more reactive to \textit{omotenashi} than their Chinese counterparts.

  Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to hard and soft attributes of a hotel. Soft attributes are those that can be changed via managerial decisions, improvement on services or small investments. On the other hand, hard attributes are elements that are impossible or highly impractical to change, such as the size of a room that has already been constructed, location of a hotel, closeness to convenient spots or elements out of the control of the hotel managers. We found that for satisfaction, Western tourists favor soft attributes, while Chinese tourists are more interested in hard attributes of hotels, consistently across price ranges. For dissatisfaction, Western tourists are also highly inclined to criticize soft attributes, such as cleanliness or the smell of cigarette in rooms. In contrast, Chinese tourists' dissatisfaction comes evenly from both hard and soft attributes.

  For hotel managers, one possible approach is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number. They are less satisfied with soft attributes, but have an identifiable method of improving satisfaction by lessening language barriers and providing a satisfactory breakfast. Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect, as well as making the hotels tobacco-free. With this strategy, we favor ``long-haul'' Western tourists who spend almost half of their budget on hotels. While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns. The reason for this being that Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased. In this paper, we provide results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan, and we can observe their stark differences and shared attributes.
